Optimal updating factor in adaptive flat-distribution-sampling simulations

### 2017-02-01 doc/invt.tex
invt.tex: small edits

For sufficiently small $\alpha(t)$,
the bias potential remains roughly the same for a short period.
%
Then,
the sampling process is approximately Markovian, % of a finite order,
and we may assume Eq. \eqref{eq:pi_p_V}
for the deterministic part
%
\begin{align}
  \langle h_i(t) \rangle
  &\approx
  \pi_i(t)
  =
  \frac{                p_i \, e^{-x_i(t)} }
       { \sum_{j = 1}^n p_j \, e^{-x_j(t)} }
  \notag
  \\
  &\approx
  p_i \,
  \left[
    1 - x_i(t) + \sum_{r=1}^n p_r \, x_r(t)
  \right]
  ,
  \label{eq:h_ave}
\end{align}
%
where we have assumed the smallness
of $x_i(t)$ in the linear expansion
and used $\sum_{j=1}^n p_j = 1$
on the second line.
%
\note{
The second step follows from
$$
\frac{ \langle h_i(t) \rangle }
     { p_i }
\approx
\frac{                       1 - x_i  }
     { \sum_{ r = 1 }^n p_r (1 - x_r) }
=
\frac{                       1 - x_i  }
     { 1 - \sum_{ r = 1 }^n p_r \, x_r }
.
$$
}%

@@

From Eqs.
\eqref{eq:v_def}-\eqref{eq:vbar_def},
\eqref{eq:rhox_sum}-\eqref{eq:h_ave},
%\eqref{eq:v_def},
%\eqref{eq:x_def},
%\eqref{eq:vbar_def},
%\eqref{eq:rhox_sum},
%\eqref{eq:vt_diffeq},
%\eqref{eq:h_split}
%\eqref{eq:h_ave},
%\eqref{eq:dvbardt},
we get a set of decoupled equations
%
\begin{equation}
  \dot x_i(t)
  =
  -\alpha(t) \, \left[ x_i(t) - \xi_i(t) \right]
  ,
\label{eq:dxdt_WL}
\end{equation}
where
\begin{equation}
  \xi_i(t)
  =
  \frac{ \zeta_i(t) }
       { p_i }
  -
  \sum_{ r = 1 }^n
    \rho_r
    \frac{ \zeta_r(t) }
         {     p_r    }
  ,
\label{eq:xi_def}
\end{equation}
%
is also a white noise as $\zeta_i(t)$.
%
\note{The derivation:
$$
\begin{aligned}
  \dot x_i
  &\stackrel{\mathrm{Eq.\; \eqref{eq:x_def}}}
            {=\joinrel=\joinrel=\joinrel=\joinrel=}
  \dot v_i - \dot{ \bar v }
  \stackrel{\mathrm{Eqs.\; \eqref{eq:vt_diffeq}\; and\; \eqref{eq:vbar_def}}}
            {=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=}
  \alpha(t) \left(
    \frac{ h_i } { p_i }
    -
    \sum_{ r = 1 }^n
      \rho_r \frac{ h_r } { p_r }
  \right)
  \\
  &\stackrel{\mathrm{Eqs.\; \eqref{eq:h_split} and \; \eqref{eq:h_ave}}}
            {=\joinrel=\joinrel=\joinrel=\joinrel=}
  \alpha(t) \left(
    \frac{ \langle h_i \rangle } { p_i }
    -
    \sum_{ r = 1 }^n
      \rho_r \frac{ \langle h_r \rangle } { p_r }
    +
    \xi_i(t)
  \right)
  \\
  &\stackrel{\mathrm{Eqs.\; \eqref{eq:rhox_sum} \;and\; \eqref{eq:h_ave}}}
            {=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=}
  \alpha(t) \left[ -x_i(t) + \xi_i(t) \right].
\end{aligned}
$$
}

@@

To do so, we first recall
the formal solution of Eq. \eqref{eq:dxdt_alpha}:
%
\begin{equation}
x(T)
=
x(0) \, e^{-q(T)}
+
\int_0^T
  \dot u\bigl( q(t) \bigr) \, \xi(t) \, dt,
\notag
%\label{eq:xt_solution}
\end{equation}
%
where
%
$
q(t) \equiv \int_0^t \alpha(t') \, dt',
$
%
and
%
\begin{align}
u(q')
&\equiv
e^{q' - q(T)}.
\label{eq:u_def}
\end{align}
%
At the end of period $T$, we have
%
\begin{align}
&\left\langle x^2(T) \right\rangle
=
\langle x^2(0) \,
\rangle e^{-2 \, q(T)}
+
\Gamma \int_0^T
  {\dot u}^2\bigl( q(t) \bigr) \,
  \, dt.
\label{eq:x2t_average}
\end{align}

@@

For the problem of
minimizing the error defined in Eq. \eqref{eq:error_sum}
for the single-bin scheme,
we note that Eq. \eqref{eq:dxdt_WL}
is of the form of Eq. \eqref{eq:dxdt_alpha}.
%
Thus,
the optimal schedule, $\alpha(t)$, is given by
Eq. \eqref{eq:alpha_invt1}
for it optimizes each term, $\langle x_i^2(T) \rangle$,
and hence the sum;
Eq. \eqref{eq:alpha_invt}
is the special case of $t_0 = 0$.
%
In Sec. \ref{sec:finlencorr},
we show that % $t_0$ can be adjusted
one can further improve the schedule by adjusting $t_0$
to accommodate the initial error.

@@

We can now simplify Eq. \eqref{eq:vt_diffeq_mbin}.
%
By using Eqs.
\eqref{eq:x_def},
\eqref{eq:vbar_def},
\eqref{eq:rhox_sum},
\eqref{eq:h_ave},
\eqref{eq:xi_def},
\eqref{eq:w_sumj},
and \eqref{eq:w_balance} we get
%
$$
\begin{aligned}
  \dot x_i(t)
  &= \alpha(t) \sum_{j=1}^n w_{ij}
  \left(
    \frac{ h_j(t) } { p_j }
    -
    \sum_{r = 1}^n
      \rho_r \frac{ h_r(t) } { p_r }
  \right)
  \\
  &\approx
  -\alpha(t) \sum_{j = 1}^n
  w_{ij} \left[ x_j(t) - \xi_j (t) \right]
  .
\end{aligned}
$$
%where
%we have expanded the right-hand side
%in linear terms of $x_j$
%on the second line.

\note{The derivative of $\dot {\bar v} = \alpha(t)$,
$$
\begin{aligned}
  \dot{ \bar v }
  &
  \stackrel{\mathrm{Eq.\; \eqref{eq:vbar_def}}}
  {=\joinrel=\joinrel=\joinrel=\joinrel=}
  \sum_{i = 1}^n \rho_i \, \dot v_i
  %
  \stackrel{\mathrm{Eq.\; \eqref{eq:vt_diffeq_mbin}}}
  {=\joinrel=\joinrel=\joinrel=\joinrel=}
  %
  \alpha(t)
  \sum_{j = 1}^n \frac{ h_j } { p_j }
                 \sum_{ i = 1 }^{n} \rho_i \, w_{ij}
  \\
  &
  \stackrel{\mathrm{Eq.\; \eqref{eq:w_balance}}}
  {=\joinrel=\joinrel=\joinrel=\joinrel=}
  \alpha(t)
  \sum_{j = 1}^n \rho_j
    \, \frac{ h_j } { p_j }
  %
  \stackrel{\mathrm{Eq.\; \eqref{eq:w_sumj}}}
  {=\joinrel=\joinrel=\joinrel=\joinrel=}
  \alpha(t)
  \sum_{j = 1}^n w_{ij}
  \sum_{r = 1}^n \rho_r
    \, \frac{ h_r } { p_r }
  .
\end{aligned}
$$
}

@@

In each class, the updating magnitudes of two schedules
of lengths $T_1$ and $T_2$
at corresponding times, $t_1/T_1 = t_2/T_2$,
are related by $T_1 \, \alpha_1 = T_2 \, \alpha_2$.
%
Further, by Eqs.
\eqref{eq:error_asym_Lagrangian}
and
\eqref{eq:Lagrangian_const},
we have
%
\begin{equation}
  \Err_A(T)
  =
  \frac { C^2 } { T }
  =
  \frac 1 T
  \left(
    \int_0^{ q(T) } M(Q) \, dQ
  \right)^2
  ,
\label{eq:error_asym2}
\end{equation}
%
which means the asymptotic error
is inversely proportional to the simulation length
for schedules in the same class,
i.e. we have the scaling relation
$T_1 \, \Err_{A1}(T_1) = T_2 \, \Err_{A2}(T_2)$.

@@

Let us now consider
simulations with the same $a_0$.
%
Since both $M(Q)$ and $m(Q)$ decrease monotonically with $Q$,
Eq. \eqref{eq:opt_qT} shows that
the optimal $q(T)$ increases with
the simulation length $T$,
more so if $M(Q)$ has a long tail.
%
This means that, if many $\lambda_k$'s are near zero,
both the optimal schedule and
normalized asymptotic error, $\Err_A(T) \cdot T$,
would be sensitive to the simulation length, $T$.
%
%If $M(Q)$ decays rapidly,
%the distribution $m(Q)$ does not critically
%depend on the cutoff $q(T)$,
%once $q(T)$ is sufficiently large.
%%
%So the optimal schedules of these simulations
%approximately satisfy the scaling relations
%described in Sec. \ref{sec:mass_distr}.
%%
%If, however, $M(Q)$ has a long tail
%because of some near-zero $\lambda_k$'s,
%increasing the simulation length $T$
%generally alters the shape of the optimal schedule.

@@

In the above section,
we have focused on
the asymptotic error.
%
By including the residual error
and minimizing the total error,
we get the optimal $t_0$,
which is, according to Eq. \eqref{eq:half_alpha0},
%
%%Assuming the system is initially equilibrated
%%under a constant updating magnitude,
%%$a_0$,
%Assuming Eq. \eqref{eq:error_res1} with
%$$
%q(T)
%=
%\int_0^T \frac{ dt } { t + t_0 }
%=
%\ln \frac{ T + t_0 } { t_0 }.
%$$
%%
%we have, from Eqs. \eqref{eq:error_split}
%and \eqref{eq:error_asym_sinc},
%%
%\begin{equation}
%  \Err
%  =
%  \Err_R + \Err_A
%  =
%  \frac { \frac 1 2 a_0 \, t_0^2 + T }
%        {          ( T + t_0 )^2          }
%  \sum_{ k = 2 }^K \Gamma_k
%  .
%\notag
%%\label{eq:error_sinc0}
%\end{equation}
%%
%The minimum is reached at
%
\begin{equation}
  t_0
  =
  \frac{  2  }
       { a_0 }
  ,
\label{eq:t0_sinc}
\end{equation}
%
and from Eqs. \eqref{eq:error_split},
\eqref{eq:error_res1},
\eqref{eq:tk0},
and
\eqref{eq:error_asym_sinc},
%
\begin{equation}
  \Err(T)
  =
  \frac{   1     }
       { T + t_0 }
  \sum_{ k = 2 }^K
    \Gamma_k
  .
\label{eq:error_sinc}
\end{equation}
%
This error decreases inversely with increasing simulation length,
as one would expect from an equilibrium FDS simulation.
%In Appendix \ref{sec:equilerr},
%we show that the above error tends
%to the error of the ideal equilibrium FDS simulation
%in the asymptotic limit.

@@

\begin{table}[h]
  \caption{\label{tab:error_Gaussian}
    Error of the Gaussian updating scheme of $\sigma = 10$.
    $t_0$ is given by Eq. \eqref{eq:t0_sinc}.
    \note{
      The data were collected in
      \texttt{data/tab1} by running
      the program \texttt{invt}.
    }%
  }
  \setlength{\tabcolsep}{2pt}
  \renewcommand\arraystretch{1.2}
  \begin{tabular} { l | p{2.2cm} p{2.4cm} p{2.0cm} }
    \hline
      Schedule
    &
      Inverse-time, \newline
      Eq. \eqref{eq:alpha_invt1}
    &
      Modified inverse-time,
      Eq.~\eqref{eq:alpha_invtlambda}
      with optimized $\lambda$
    &
      Optimal, \newline
      Eq. \eqref{eq:q_opt}
    \\
    \hline
    Global
    &
    $4.36(9) \times 10^{-6}$
    &
    $7.1(1) \times 10^{-7}$
    &
    $2.6(1) \times 10^{-7}$
    \\
    \hline
    Local
    &
    $3.83(7) \times 10^{-4}$
    &
    $1.72(4) \times 10^{-4}$
    &
    $9.1(2) \times 10^{-5}$
    \\
    \hline
  \end{tabular}
\end{table}

@@

We thank Dr. Y. Mei, J. Wang,
O. Nassar, Dr. C. Lai, Dr. S. Ou, D. Stuhlsatz,
Dr. C. Myers, and Dr. O. Samoylova
for helpful discussions.  We gratefully acknowledge the Robert A. Welch Foundation (H-0037), the National Science Foundation (CHE-1152876) and the National Institutes of Health (GM-037657) for partial support of this work.  This research used computing resources of the National Science Foundation XSEDE grid.

>>>>

For sufficiently small $\alpha(t)$,
the bias potential remains roughly the same for a short period.
%
Then,
the sampling process is approximately Markovian, % of a finite order,
and we may assume Eq. \eqref{eq:pi_p_V}
for the deterministic part
%
\begin{align}
  \langle h_i(t) \rangle
  &\approx
  \pi_i(t)
  =
  \frac{                p_i \, e^{-x_i(t)} }
       { \sum_{j = 1}^n p_j \, e^{-x_j(t)} }
  \notag
  \\
  &\approx
  p_i \,
  \left[
    1 - x_i(t) + \sum_{j = 1}^n p_j \, x_j(t)
  \right]
  ,
  \label{eq:h_ave}
\end{align}
%
where we have assumed the smallness
of $x_i(t)$ in the linear expansion
and used $\sum_{j=1}^n p_j = 1$
on the second line.
%
\note{
The second step follows from
$$
\frac{ \langle h_i(t) \rangle }
     { p_i }
\approx
\frac{                       1 - x_i  }
     { \sum_{ r = 1 }^n p_j (1 - x_j) }
=
\frac{                       1 - x_i  }
     { 1 - \sum_{ j = 1 }^n p_j \, x_j }
.
$$
}%

@@

From Eqs.
\eqref{eq:v_def}-\eqref{eq:vbar_def},
\eqref{eq:rhox_sum}-\eqref{eq:h_ave},
%\eqref{eq:v_def},
%\eqref{eq:x_def},
%\eqref{eq:vbar_def},
%\eqref{eq:rhox_sum},
%\eqref{eq:vt_diffeq},
%\eqref{eq:h_split}
%\eqref{eq:h_ave},
%\eqref{eq:dvbardt},
we get a set of decoupled equations
%
\begin{equation}
  \dot x_i(t)
  =
  -\alpha(t) \, \left[ x_i(t) - \xi_i(t) \right]
  ,
\label{eq:dxdt_WL}
\end{equation}
where
\begin{equation}
  \xi_i(t)
  =
  \frac{ \zeta_i(t) }
       { p_i }
  -
  \sum_{ j = 1 }^n
    \rho_j
    \frac{ \zeta_j(t) }
         {     p_j    }
  ,
\label{eq:xi_def}
\end{equation}
%
is also a white noise as $\zeta_i(t)$,
i.e. we may write
$$
  \langle \xi_i(t) \, \xi_i(t') \rangle = \Gamma_i \, \delta(t - t'),
$$
for some $\Gamma_i$.
%
\note{The derivation:
$$
\begin{aligned}
  \dot x_i
  &\stackrel{\mathrm{Eq.\; \eqref{eq:x_def}}}
            {=\joinrel=\joinrel=\joinrel=\joinrel=}
  \dot v_i - \dot{ \bar v }
  \stackrel{\mathrm{Eqs.\; \eqref{eq:vt_diffeq}\; and\; \eqref{eq:vbar_def}}}
            {=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=}
  \alpha(t) \left(
    \frac{ h_i } { p_i }
    -
    \sum_{ j = 1 }^n
      \rho_j \frac{ h_j } { p_j }
  \right)
  \\
  &\stackrel{\mathrm{Eqs.\; \eqref{eq:h_split} \; and \; \eqref{eq:xi_def}}}
            {=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=}
  \alpha(t) \left(
    \frac{ \langle h_i \rangle } { p_i }
    -
    \sum_{ j = 1 }^n
      \rho_j \frac{ \langle h_j \rangle } { p_j }
    +
    \xi_i(t)
  \right)
  \\
  &\stackrel{\mathrm{Eqs.\; \eqref{eq:h_ave} \;and\; \eqref{eq:rhox_sum}}}
            {=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=\joinrel=}
  \alpha(t) \left[ -x_i(t) + \xi_i(t) \right].
\end{aligned}
$$
}

@@

To do so, we first recall
the formal solution of Eq. \eqref{eq:dxdt_alpha}:
%
\begin{equation}
x(T)
=
x(0) \, e^{-q(T)}
+
\int_0^T
  \dot u\bigl( q(t) \bigr) \, \xi(t) \, dt,
\notag
%\label{eq:xt_solution}
\end{equation}
%
where
%
$
q(t) \equiv \int_0^t \alpha(t') \, dt',
$
%
and
%
\begin{align}
u(q')
&\equiv
e^{q' - q(T)}.
\label{eq:u_def}
\end{align}
%
At the end of period $T$, we have
%
\begin{align}
  &\left\langle x^2(T) \right\rangle
  =
  \langle x^2(0) \rangle \, e^{-2 \, q(T)}
  +
  \Gamma \int_0^T
    {\dot u}^2\bigl( q(t) \bigr) \,
    \, dt.
  \label{eq:x2t_average}
\end{align}

@@

For the problem of
minimizing the error defined in Eq. \eqref{eq:error_sum}
for the single-bin scheme,
we note that Eq. \eqref{eq:dxdt_WL}
is of the form of Eq. \eqref{eq:dxdt_alpha}.
%
Thus,
the optimal schedule, $\alpha(t)$, is given by
Eq. \eqref{eq:alpha_invt1}
for it optimizes each term, $\langle x_i^2(T) \rangle$,
and hence the sum;
Eq. \eqref{eq:alpha_invt}
is the special case of $t_0 = 0$.

%In Sec. \ref{sec:finlencorr},
%we show that % $t_0$ can be adjusted
%one can further improve the schedule by adjusting $t_0$
%to accommodate the initial error.
To find the optimal value of $t_0$,
we use the optimal schedule in Eq. \eqref{eq:x2t_average},
and
$$
\left\langle x^2(T) \right\rangle
=
\frac{ \left\langle x^2(0) \right\rangle \, t_0^2 }
     { (t_0 + T)^2 }
+
\frac{ \Gamma \, T}
     { (t_0 + T)^2 }
.
$$
Using this result for each $x_i$,
we get the final total error, $E(T)$,
as defined in Eq. \eqref{eq:error_sum},
\begin{equation}
  E(T)
  =
  \frac{ \sum_{i=1}^n \left\langle x_i^2(0) \right\rangle \, t_0^2 }
       { (t_0 + T)^2 }
  +
  \frac{ \sum_{i=1}^n \Gamma_i \, T}
       { (t_0 + T)^2 }
  .
  \label{eq:error_singlebin}
\end{equation}
%
This error is minimized if
%
\begin{equation}
t_0 = \frac{ \sum_{i = 1}^n \Gamma_i }
           { \sum_{i = 1}^n \left\langle x_i^2(0) \right\rangle }
           ,
  \label{eq:t0_singlebin}
\end{equation}
%
and at this point
%
\begin{equation}
  E(T)
  =
  \frac{ 1 } { T + t_0 }
  \sum_{i = 1}^n \Gamma_i
  .
  \label{eq:Emin_singlebin}
\end{equation}

@@

We can now simplify Eq. \eqref{eq:vt_diffeq_mbin}.
%
By using Eqs.
\eqref{eq:v_def}, \eqref{eq:vbar_def},
\eqref{eq:vt_diffeq_mbin}-\eqref{eq:w_balance}
we get
%
\begin{align*}
  \dot{ \bar v }(t)
  =
  \alpha(t)
  \sum_{r = 1}^n \rho_r
    \, \frac{ h_r(t) } { p_r }
  =
  \alpha(t)
  \sum_{j = 1}^n w_{ij}
  \sum_{r = 1}^n \rho_r
    \, \frac{ h_r(t) } { p_r }
  ,
\end{align*}
%
\note{Derivation.
$$\begin{aligned}
  \dot{ \bar v }
  &
  \stackrel{\mathrm{Eq.\; \eqref{eq:vbar_def}}}
  {=\joinrel=\joinrel=\joinrel=\joinrel=}
  \sum_{i = 1}^n \rho_i \, \dot v_i
  %
  \stackrel{\mathrm{Eq.\; \eqref{eq:vt_diffeq_mbin}}}
  {=\joinrel=\joinrel=\joinrel=\joinrel=}
  %
  \alpha(t)
  \sum_{j = 1}^n \frac{ h_j } { p_j }
                 \sum_{ i = 1 }^{n} \rho_i \, w_{ij}
  \\
  &
  \stackrel{\mathrm{Eq.\; \eqref{eq:w_balance}}}
  {=\joinrel=\joinrel=\joinrel=\joinrel=}
  \alpha(t)
  \sum_{j = 1}^n \rho_j
    \, \frac{ h_j } { p_j }
  %
  \stackrel{\mathrm{Eq.\; \eqref{eq:w_sumj}}}
  {=\joinrel=\joinrel=\joinrel=\joinrel=}
  \alpha(t)
  \sum_{j = 1}^n w_{ij}
  \sum_{r = 1}^n \rho_r
    \, \frac{ h_r } { p_r }
  .
\end{aligned}$$
}
%
and by Eqs. \eqref{eq:x_def}, \eqref{eq:rhox_sum} and \eqref{eq:h_ave},
%
$$
\begin{aligned}
  \dot x_i(t)
  &= \alpha(t) \sum_{j=1}^n w_{ij}
  \left(
    \frac{ h_j(t) } { p_j }
    -
    \sum_{r = 1}^n
      \rho_r \frac{ h_r(t) } { p_r }
  \right)
  \\
  &\approx
  -\alpha(t) \sum_{j = 1}^n
  w_{ij} \bigl[ x_j(t) - \xi_j (t) \bigr]
  .
\end{aligned}
$$
%where
%we have expanded the right-hand side
%in linear terms of $x_j$
%on the second line.

@@

In each class, the updating magnitudes of two schedules
of lengths $T_1$ and $T_2$
at corresponding times, $t_1/T_1 = t_2/T_2$,
are related by $T_1 \, \alpha_1(t_1) = T_2 \, \alpha_2(t_2)$.
%
Further, by Eqs.
\eqref{eq:error_asym_Lagrangian}
and
\eqref{eq:Lagrangian_const},
we have
%
\begin{equation}
  \Err_A(T)
  =
  \frac { C^2 } { T }
  =
  \frac 1 T
  \left(
    \int_0^{ q(T) } M(Q) \, dQ
  \right)^2
  ,
\label{eq:error_asym2}
\end{equation}
%
which means that the asymptotic error
is inversely proportional to the simulation length
for schedules in the same class.
%which can be rephrased as another scaling relation
%$$
%T_1 \, \Err_{A1}(T_1) = T_2 \, \Err_{A2}(T_2).
%$$

@@

For simulations with the same $a_0$,
the shape of the mass distribution, $m(Q)$,
also determines how much the optimal schedule
would depend on the simulation length, $T$.
%
Since both $M(Q)$ and $m(Q)$ decrease monotonically with $Q$,
Eq. \eqref{eq:opt_qT} shows that
the optimal $q(T)$ increases with
the simulation length, $T$,
more so if $M(Q)$ has a long tail.
%
Thus, if $M(Q)$ decays slowly because of
many near zero eigenvalues, $\lambda_k$'s (as in the metadynamics case),
both the optimal schedule and
normalized asymptotic error, $\Err_A(T) \cdot T$,
would be sensitive to the simulation length, $T$.
%
In contrast, if all eigenvalues are $1.0$
as in the single-bin or WL updating scheme discussed previously,
the optimal schedule is
given by the universal inverse-time formula,
Eq. \eqref{eq:alpha_invt1},
and the normalized asymptotic error
is roughly a constant
[cf. Eq. \eqref{eq:error_singlebin}].
%
%If $M(Q)$ decays rapidly,
%the distribution $m(Q)$ does not critically
%depend on the cutoff $q(T)$,
%once $q(T)$ is sufficiently large.
%%
%So the optimal schedules of these simulations
%approximately satisfy the scaling relations
%described in Sec. \ref{sec:mass_distr}.
%%
%If, however, $M(Q)$ has a long tail
%because of some near-zero $\lambda_k$'s,
%increasing the simulation length $T$
%generally alters the shape of the optimal schedule.

@@

In the above section,
we have focused on
the asymptotic error.
%
By including the residual error
and minimizing the total error,
we get the optimal $t_0$,
which is, according to Eq. \eqref{eq:half_alpha0},
%
%%Assuming the system is initially equilibrated
%%under a constant updating magnitude,
%%$a_0$,
%Assuming Eq. \eqref{eq:error_res1} with
%$$
%q(T)
%=
%\int_0^T \frac{ dt } { t + t_0 }
%=
%\ln \frac{ T + t_0 } { t_0 }.
%$$
%%
%we have, from Eqs. \eqref{eq:error_split}
%and \eqref{eq:error_asym_sinc},
%%
%\begin{equation}
%  \Err
%  =
%  \Err_R + \Err_A
%  =
%  \frac { \frac 1 2 a_0 \, t_0^2 + T }
%        {          ( T + t_0 )^2          }
%  \sum_{ k = 2 }^K \Gamma_k
%  .
%\notag
%%\label{eq:error_sinc0}
%\end{equation}
%%
%The minimum is reached at
%
\begin{equation}
  t_0
  =
  \frac{  2  }
       { a_0 }
  .
\label{eq:t0_sinc}
\end{equation}
%
For the single-bin updating scheme,
it recovers Eq. \eqref{eq:t0_singlebin}
under the assumption of Eq. \eqref{eq:y2_eql}.
%
From Eqs. \eqref{eq:error_split},
\eqref{eq:error_res1},
\eqref{eq:tk0},
and
\eqref{eq:error_asym_sinc},
we get
%
\begin{equation}
  \Err(T)
  =
  \frac{   1     }
       { T + t_0 }
  \sum_{ k = 2 }^K
    \Gamma_k
  .
\label{eq:error_sinc}
\end{equation}
%
which serves as a generalization of
the result from the single-bin scheme, Eq. \eqref{eq:Emin_singlebin}.
%
This error decreases with increasing simulation length,
as one would expect from an equilibrium FDS simulation.
%In Appendix \ref{sec:equilerr},
%we show that the above error tends
%to the error of the ideal equilibrium FDS simulation
%in the asymptotic limit.

@@

\begin{table}[h]\footnotesize
  \caption{\label{tab:error_Gaussian}
    Error of the Gaussian updating scheme of $\sigma = 10$
    under different updating schedules.
    In Eqs. \eqref{eq:alpha_invt1} and \eqref{eq:alpha_invtlambda},
    $t_0$ is given by Eq. \eqref{eq:t0_sinc};
    and in Eq. \eqref{eq:alpha_invtlambda},
    the optimal value of $\lambda$ is used.
    \note{\newline
      The data were collected in
      \texttt{data/tab1} by running
      the program \texttt{invt}.
    }%
  }
  \setlength{\tabcolsep}{2pt}
  \renewcommand\arraystretch{1.2}
  \begin{tabular} { l | p{2.2cm} p{2.4cm} p{2.0cm} }
    \hline
      Schedule
    &
      Inverse-time, \newline
      Eq. \eqref{eq:alpha_invt1}
    &
      Modified, \newline
      Eq.~\eqref{eq:alpha_invtlambda}
    &
      Optimal, \newline
      Eq. \eqref{eq:q_opt}
    \\
    \hline
    Global
    &
    $4.36(9) \times 10^{-6}$
    &
    $7.1(1) \times 10^{-7}$
    &
    $2.6(1) \times 10^{-7}$
    \\
    \hline
    Local
    &
    $3.83(7) \times 10^{-4}$
    &
    $1.72(4) \times 10^{-4}$
    &
    $9.1(2) \times 10^{-5}$
    \\
    \hline
  \end{tabular}
\end{table}

@@

We thank Dr. Y. Mei, J. Wang,
O. Nassar, Dr. C. Lai, Dr. S. Ou, D. Stuhlsatz,
Dr. C. Myers, and Dr. O. Samoylova
for helpful discussions.
%
We gratefully acknowledge the Robert A. Welch Foundation (H-0037),
the National Science Foundation (CHE-1152876)
and the National Institutes of Health (GM-037657)
for partial support of this work.
%
JM thanks support from the National Institutes of Health (R01-GM067801, R01-GM116280),
the Welch Foundation (Q-1512),
and National Science Foundation (Grant PHY-1427654).
%
This research used computing resources of the National Science Foundation XSEDE grid.
%
%
